\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2018-06-08 doc/USER_MANUAL/11_graphics.tex
added a sentence about ParaView to the users manual
fixed the USE_VTK_INSTEAD_OF_MESH issue reported by Huihui

@@

At the beginning of the source file \texttt{combine\_vol\_data.f90} (located in \texttt{src/auxiliaries/}), there is a logical constant parameter \texttt{USE\_VTK\_OUTPUT} whose default value is \texttt{.true.}, that which will provide the output combined file directly in the VTK format and you can use Paraview to visualize it.

@@

If the value of this parameter is \texttt{.false.}, the output mesh file will have the name \texttt{velocity\_Z\_it000400.mesh}. Then we next have to convert the
\texttt{.mesh} file into the VTU (Unstructured grid file) format which can be viewed in ParaView.

\noindent
For this task, you can use and modify the
script \texttt{mesh2vtu.pl} located in directory \texttt{\small utils/Visualization/Paraview/}, for example:

@@

Notice that this Perl script uses a program \texttt{mesh2vtu} in the \texttt{utils/Visualization/Paraview/mesh2vtu} directory, which further
uses the VTK \urlwithparentheses{http://www.vtk.org/} run-time library for its execution. Therefore, make sure you have them properly set
in the script according to your system.

>>>>

{\red To visualize seismograms with Paraview, you should turn off the flag SU\_FORMAT, and turn on the use binary seismograms flag. This will generate .bin files, that you can open with Paraview. You have to select the way you open it ("raw"), and specify the dimensions of the file (NSTEP and NREC).}

@@

At the beginning of the source file \texttt{src/auxiliaries/combine\_vol\_data\_impl.f90} there is a logical parameter \texttt{USE\_VTK\_INSTEAD\_OF\_MESH},
whose default value is \texttt{.false.}, which can be used to generate the combined output file directly in VTK format, which can then be visualized using Paraview.

@@

If the value of this parameter is \texttt{.false.}, the output mesh file will have a name of the form \texttt{velocity\_Z\_it000400.mesh}.
One then has to convert the \texttt{.mesh} file into the VTU (Unstructured grid file) format which can be viewed in ParaView.

\noindent
For this task, you can use and modify the
script \texttt{mesh2vtu.pl} located in directory \texttt{\small utils/Visualization/Paraview}, for example:

@@

Notice that this Perl script uses a program \texttt{mesh2vtu} in the \texttt{utils/Visualization/Paraview/mesh2vtu} directory, which further
uses the VTK \urlwithparentheses{http://www.vtk.org} run-time library for its execution. Therefore, make sure you have them properly set
in the script according to your system.
